---
title: "Regression Models Course Project"
author: "Chiu Wei Chieh"
output: pdf_document
---
```{r echo = F, warning=F, error=F, message=F}
require(knitr); require(ggplot2); require("GGally")
opts_chunk$set(warning=F, error=F, message=F, fig.width = 10, fig.height = 4, results='asis', cache = F, tidy = F)
```

> ### Question 1 : Is an automatic or manual transmission better for MPG?
> ### Question 2 : Quantify the MPG difference between automatic and manual transmissions.

My strategy :  
1. Explore the relationship between mpg and other variables.  
2. Fit multiple models and diagnose with redidual plots and nested model testing.   
3. Select a suitable model and answer the questions.  

### 1. Exploratory

```{r results='hide'}
library(datasets); data(mtcars)
fitAll <- lm(mpg ~ ., data = mtcars)
summary(fitAll)$coef
```
From the summary of all variables, we have the estimate beta value(absolute value) in decreasing order :  
wt > am > qsec > drat > gear > vs > carb > cyl > hp > disp  

Figure 1 & 2 : Manual transmission seems have better MPG.   
Figure 3 : wt and mpg is negative correlation. Automatic transmission cars is heavier.  
Figure 4 : qsec and mpg is positive correlation.  

### 2. Fit models and diagnose

**Nested model testing 1:  **
```{r echo=FALSE, results='markup'}
fitAm <- lm(mpg ~ factor(am), data = mtcars)
fit1 <- update(fitAm, mpg ~ factor(am) + wt)
fit2 <- update(fitAm, mpg ~ factor(am) + wt + qsec)
fit3 <- update(fitAm, mpg ~ factor(am) + wt + qsec + drat)
fit4 <- update(fitAm, mpg ~ factor(am) + wt + qsec + drat + gear + vs + carb + cyl + hp + disp)
anova(fitAm, fit1, fit2, fit3, fit4)
```
**Diagnose 1**: In the mpg ~ am + wt model, am seems have no significant effect on mpg(Figure 5). But mpg ~ am + qsec model shows am has significant effect on mpg(Figure 6). And considering the result of the first nested model testing, our model should include am, wt and qsec.  

**Nested model testing 2(am, wt, qsec and their interactions) : **
```{r echo=FALSE, results='markup'}
fit5 <- update(fitAm, mpg ~ factor(am) + wt + factor(am)*wt)
fit6 <- update(fitAm, mpg ~ factor(am) + wt + factor(am)*wt + qsec)
fit7 <- update(fitAm, mpg ~ factor(am) + wt + factor(am)*wt + qsec + factor(am)*qsec)
fit8 <- update(fitAm, mpg ~ factor(am) + wt + factor(am)*wt + qsec + factor(am)*qsec + wt*qsec)
anova(fitAm, fit1, fit5, fit6, fit7, fit8)
```    
**Diagnose 2**: Compare model with and without am*wt term. The result shows that it has great effect on model. So we want to include this term. 
```{r echo=FALSE, results='markup'}
data.frame(withAmWt = round(summary(fit2)$coef[2,1], 3), withoutAmWt = round(summary(fit6)$coef[2,1], 3))
```
**Diagnose 3**: Both am\*qsec and wt\*qsec has no significant effect on model.

### 3. Model of choice
fit6 <- lm(mpg ~ factor(am) + wt+ qsec + factor(am)*wt, data = mtcars)
```{r results='markup'}
summary(fit6)$coef
```

> ### Answer 1 : According to our model, manual transmission is better for MPG than automatic transmission.  
> ### Answer 2 : Holding other variables in constant, the mpg difference between manual and automatic transmission is 14.079 miles/gallon with standard error 3.435.
    
### Appendix

**Figure 1**
```{r}
g <- ggplot(data = mtcars, aes(y = mpg, x = factor(am)))
g <- g + geom_violin(aes(fill = factor(am)))
g
```
**Figure 2**
```{r}
g <- ggplot(data = mtcars, aes(y = mpg, x = factor(am)))
g <- g + geom_point(aes(fill = wt)) + geom_smooth(method = lm)
g
```
**Figure 3**
```{r}
g <- ggplot(data = mtcars, aes(y = mpg, x = wt))
g <- g + geom_point(aes(colour = factor(am))) + geom_smooth(method = lm)
g
```
**Figure 4**
```{r}
g <- ggplot(data = mtcars, aes(y = mpg, x = qsec))
g <- g + geom_point(aes(colour = factor(am))) + geom_smooth(method = lm)
g
```
**Figure 5**
```{r}
dataResid <- data.frame(y = resid(lm(mpg ~ wt, data=mtcars)), x = resid(lm(am ~ wt, data=mtcars)))
g <- ggplot(data = dataResid, aes(y = y, x = x))
g <- g + geom_point() + geom_smooth(method = lm)
g
```
**Figure 6**
```{r}
dataResid <- data.frame(y = resid(lm(mpg ~ qsec, data=mtcars)), x = resid(lm(am ~ qsec, data=mtcars)))
g <- ggplot(data = dataResid, aes(y = y, x = x))
g <- g + geom_point() + geom_smooth(method = lm)
g
```
